An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-22 VLDB2026/main.tex
change

>>>>

	\textit{\textbf{\textcolor{red}{Large-scale Datasets.}}} \textcolor{red}{As shown in the figure~\ref{fig:Big Dataset range}, in the 100-million-scale dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged. However, their high performance is achieved at the cost of extremely high memory consumption (300-400GB). At the same time, we can see that some algorithms (e.g., SeRF, ACORN-1) perform even worse than the VBASE database, which indicates that they do not adapt well to large-scale dataset scenarios. Although Milvus has a low QPS, it can achieve a recall of 1 with an excellent memory footprint of around 80GB}.
